A properly labelled proof system for intuitionistic modal logics

### 2019-09-24 caleidoscope/caleidoscope.tex
missing proof of completeness added and small modif

\begin{center}
	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{\lb y \mbox{ fresh}}
		{\Rightarrow \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
		{\vlin {\rlabrn{\BOX}}
			{\lb z, \lb w \mbox{ fresh}}
			{\futs xy, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{y}{\BOX (A \IMP B)}}
			{\vlin {\rlabrn{\IMP}}
				{\lb u \mbox{ fresh}}
				{\futs xy, \futs yz, \accs zw, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{w}{A \IMP B}}
				{\vlin {\color{red}{\rn{F_1}}}
					{}
					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
					{\vlin {\rn{trans}}
						{}
						{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
						{\vliin {\llabrn{\IMP}}
							{}
							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
							{\vlhy{\circledast  \hspace{75mm}}}
							{\vlhy{\star}}}}}}}
	}$

@@

The derivation continues as the result of applying the rule $\llabrn{\IMP}$. From this rule we obtain two trees:

On one side, the derivation that follows from $\circledast$:

	$
	\vlderivation{
		\vlin{\llabrn{\IMP}}{}{\circledast}{\vlin {\rlabrn{\DIA}}
			{}
			{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
			{\vlin {\rn{refl}}
				{}
				{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
				{\vlin {\rn{id}}
					{}
					{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \futs uu, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
					{\vlhy {}}}}}
	}$
\end{center}

@@

Following the proof for the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.

@@

	\todo{say that we can obtain the proof for monotonicity using the proof of cut.}

>>>>

\begin{center}
	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{\lb y \mbox{ fresh}}
		{\Rightarrow \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
		{\vlin {\rlabrn{\BOX}}
			{\lb z, \lb w \mbox{ fresh}}
			{\futs xy, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{y}{\BOX (A \IMP B)}}
			{\vlin {\rlabrn{\IMP}}
				{\lb u \mbox{ fresh}}
				{\futs xy, \futs yz, \accs zw, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{w}{A \IMP B}}
				{\vlin {\color{red}{\rn{F_1}}}
					{}
					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
					{\vlin {\rn{trans}}
						{}
						{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
						{\vliin {\llabrn{\IMP}}
							{}
							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
							{\vlin {\rlabrn{\DIA}}
									{}
									{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
									{\vlin {\rn{refl}}
										{}
										{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
										{\vlin {\rn{id}}
											{}
											{R, \futs uu,  \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
											{\vlhy {}}}}}
							{\vlin {\rn{refl}}
								{}
								{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
								{\vlin {\llabrn{\BOX}}
									{}
									{R, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
									{\vlin {\rn{refl}}
										{}
										{R, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
										{\vlin {\rn{id}}
											{}
											{R, \futs tt, \futs uu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
											{\vlhy {}}}}}}}}}}}
	}$

@@

where $R$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.

@@

Following the proof of the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.

@@

	\todo{say that we can obtain the proof of monotonicity using the proof of cut.}
